Introducing Distributed Dynamic Data-intensive (D3) Science: Understanding Applications and Infrastructure

### 2015-09-12 3dpas_intro.tex
checkpoint.

%   Many problems at the forefront of science, engineering, medicine,
%   and the social sciences are increasingly complex and
%   interdisciplinary due to the plethora of data sources and
%   computational methods available today.  A common feature across many
%   of these problems is the amount and diversity of data and
%   computation that must be integrated to yield insights. Such data is
%   increasingly large-scale and distributed: the datasets, their
%   locations, and associated scheduling decisions are
%   time-dependent.

>>>>

  A common feature across many science and engineering applications is the
  amount and diversity of data and computation that must be integrated to yield
  insights. Often data is increasingly large-scale and distributed. Often the
  datasets, their locations, availability, analysis and associated scheduling
  decisions are time-dependent. Collectively these give rise to dynamic
  distributed data intensive applications. This paper attempts to survey several
  such applications, to provide a common conceptual framework to understand them
  as well as examine the infrastructure used in support of applications.
  Whereas the analysis of large volumes of ``static'' data have received
  significant attention, the ability to manage large-volumes of dynamic and
  distributed data is more primitive. This work will ameliorate the state.
